Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-07 paper/HH4b.tex
Divided results of PU section among independent sections
Implemented comments from Nathan

\documentclass[a4paper,11pt]{article}
\usepackage{jheppub}
\usepackage{graphicx}% Include figure files
\usepackage{graphics}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{epstopdf}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage[pdftex]{hyperref}
\usepackage{natbib}

@@

\bibliographystyle{JHEP}
\usepackage{multirow}

@@

\abstract{
  The measurement of Higgs pair production is one of the cornerstones of
  the LHC program for the next years.
  %
  Double Higgs production provides a unique window to the electroweak
  symmetry breaking mechanism, and in particular it allows
  to access the Higgs trilinear coupling.
  %
  In this work we study the feasibility of the observation of the production of
  Higgs boson pairs at the High-Luminosity LHC (HL-LHC) in the
  $b\bar{b}b\bar{b}$ final state.
  %
  While the signal in this channel
  is enhanced by the large branching fraction of Higgs bosons to
  $b\bar{b}$ pairs, the measurement is  challenging due to the
  overwhelming QCD multijet background.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with modern multivariate techniques, which lead to a substantial
  enhacement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes that is found
  to be as important or even dominant over the irreducible $4b$ QCD background.
  %
  We demonstrate the robustness of our analysis under realistic
  pile-up conditions expected at the HL-LHC.
  %
   By combining the contribution from the boosted, intermediate and resolved
  topologies we obtain a signal significance of $S/\sqrt{B}\simeq 4$.
  %
  Our analysis indicates
  that the $b\bar{b}b\bar{b}$ channel 
  should be enough claim evidence for
  the observation of double Higgs production
  at the HL-LHC.
}

@@

\input{sec-intro}
\input{sec-mcsamples}
\input{sec-analysis}
\input{sec-results}
\input{sec-mva}
\input{sec-pileup}
\input{sec-conclusions}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage{jheppub}
\usepackage{graphicx}% Include figure files
\usepackage{graphics}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{epstopdf}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage[pdftex]{hyperref}
\usepackage{natbib}
\usepackage{multirow}

@@

\bibliographystyle{JHEP}

@@

\abstract{
  The measurement of Higgs pair production is one of the cornerstones of
  the LHC program for the next years.
  %
  Double Higgs production provides a unique window to the electroweak
  symmetry breaking mechanism, and in particular it allows
  to access the Higgs trilinear coupling.
  %
  In this work we study the feasibility of the observation of the production of
  Higgs boson pairs at the High-Luminosity LHC (HL-LHC) in the
  $b\bar{b}b\bar{b}$ final state.
  %
  While the signal in this channel
  is enhanced by the large branching fraction of Higgs bosons to
  $b\bar{b}$ pairs, the measurement is  challenging due to the
  overwhelming QCD multijet background.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with modern multivariate techniques, which lead to a substantial
  enhacement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes that is found
  to be as important or even dominant over the irreducible $4b$ QCD background.
  %
  We demonstrate the robustness of our analysis under realistic
  pile-up conditions expected at the HL-LHC.
  %
  For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
  combining the contributions from the boosted, intermediate and resolved
  topologies we obtain a signal significance of $S/\sqrt{B}\simeq 4$.
  %
  Our analysis indicates
  that the $b\bar{b}b\bar{b}$ channel
alone should allow the observation of double Higgs production
  at the HL-LHC.
}

@@

\input{sec-intro}
\input{sec-mcsamples}
\input{sec-analysis}
\input{sec-results}
\input{sec-mva}
\input{sec-conclusions}

### 2015-12-07 paper/sec-analysis.tex
Implemented comments from Nathan

\subsection{Motivation for kinematical cuts}

@@

To study the impact of PU in our analysis,
Minimum Bias (MB) events,
including Multiple Parton Interactions (MPI), have been generated
with {\tt Pythia8}, and
superimposed to the signal
and background samples described in Sect.~\ref{mcgeneration}.
%
We have explored two scenarios for the amount of PU expected
at the HL-LHC, one with a mean number of
PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$, and another
with $\la n_{\rm PU}\ra=150$.
%
In order to subtract the PU, a number of techniques
have been developed
recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  will be subtracted by means
of the the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet}.
%

>>>>

\subsection{Motivation for basic kinematical cuts}

@@

To study the impact of PU in our analysis,
Minimum Bias (MB) events,
including Multiple Parton Interactions (MPI), have been generated
with {\tt Pythia8}, and
superimposed to the signal
and background samples described in Sect.~\ref{mcgeneration}.
%
We have explored two scenarios for the impact
of PU in our analysis,
one with a mean number of
PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$, and another
with $\la n_{\rm PU}\ra=150$.
%
In order to subtract the PU, a number of techniques
have been developed
recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  will be subtracted by means
of the the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet}.
%

### 2015-12-07 paper/sec-intro.tex
Divided results of PU section among independent sections
Implemented comments from Nathan

The measurement of double Higgs production will be one of the main
physics goals of the LHC program in its recently started high-energy
phase, as well as for its future high-luminosity upgrade (HL-LHC),
which aims to accumulate a total integrated
luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta,CMS:2013xfa}.
%
Higgs pair production is directly sensitive to the
Higgs trilinear coupling $\lambda$~\cite{baglio}, and thus 
provides crucial
information on the electroweak symmetry breaking mechanism.
%
It is also sensitive to the underlying strength of the Higgs interactions
at high energies, and can be used to test the composite nature of the 
Higgs boson~\cite{Giudice:2007fh,Contino:2010mh}.
%
While Standard Model (SM) cross-sections are small,
many Beyond the SM (BSM)
scenarios predict enhanced rates for double Higgs production, and
thus searches for this process have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
and will continue at Run II.
%
In addition, Higgs pair production will also be a central process at
any future high-energy 
collider, either at a 100 TeV circular machine~\cite{Barr:2014sga,Papaefstathiou:2015iba,Azatov:2015oxa} or at
a linear or circular electron-positron collider~\cite{Contino:2013gna}.

As in the case of single Higgs production,
in the SM the dominant mechanism for the production of a pair of Higgs bosons at the LHC is 
gluon fusion (see Ref.~\cite{baglio,Frederix:2014hta} and references therein), analogously to single
Higgs production~\cite{Dittmaier:2012vm}.
%
For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once NNLL corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in gluon fusion have been performed for several different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
%
While these studies differ in their qualitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$
will only be achieved from the combination of various final states.

In addition to the gluon-fusion production mode, Higgs pairs
can be also produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes $hhW$ and $hhZ$~\cite{Barger:1988jk,baglio}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
Concentrating on the SM dynamics of Higgs pair production
in different channels, several studies
have investigate the interplay of various kinematical
distributions towards the optimisation of the
extraction of $\lambda$ from the measured
cross-sections, as well as the improvement
in the signal modeling taking into account
higher-order corrections and theoretical
uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
%

@@

In the context of SM production,
the main advantage of the $b\bar{b}b\bar{b}$ final state is the
enhancement of the signal yield
from the large branching fraction of Higgs bosons into bottom-anti-bottom
pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
%
However, a measurement in this channel
needs to deal with an overwhelming QCD multi-jet background.
%
Recent studies of Higgs pair production in this
final state~\cite{Wardrope:2014kya,deLima:2014dta}
estimate that, for an integrated
luminosity of
$\mathcal{L}_{\rm int}$=3000 fb$^{-1}$,
a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
%
These studies are
based on exploiting the differences between signal and background
using techniques that account for a large number of kinematic
variables, Boosted Decision Trees
and Shower Deconstruction~\cite{Soper:2011cr} respectively.
%
While irreducible backgrounds, such as $4b$ and
$t\bar{t}$, are included, the contribution
from reducible processes, such as $bbjj$ and
$jjjj$, which can fake the signal when 
light jets are mistagged as $b$-jets, are not accounted for.
%
As will show, this approximation is not justified since, both due to
combinatorics and to $b$-quark radiation in the shower, the
contribution of the $2b2j$ and $4j$ backgrounds can become comparable or even larger
than the irreducible $4b$ component.

In this work, we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $b\bar{b}b\bar{b}$ final state.
%
 Our strategy is based on a combination of traditional cut-based
 methods with modern multivariate analysis (MVA),
 leading to a substantial
  enhancement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes.
  %
  We also model the impact of the pile-up (PU) effects expected at the
  HL-LHC by means of modern PU subtraction techniques.
  %
  By combining the contribution from the boosted, intermediate and resolved
  topologies we achieve a total signal significance of $S/\sqrt{B}\simeq 4.0$
  for $\mathcal{L}_{\rm int}$=3000 fb$^{-1}$.
%
  These results emphasize the crucial importance that the $b\bar{b}b\bar{b}$ final state
  has for studies of Higgs pair production and for the determination of
  $\lambda$, as well as the advantages of the use of modern statistical
  analysis methods.

The structure of this paper is the following.
%
In Sect.~\ref{mcgeneration} we discuss the modeling of the signal
and background processes using Monte Carlo event generators.
%
In Sect.~\ref{sec:analysis}
we introduce our analysis strategy, and in particular
the classification of each individual event into
different categories according to their topology.
%
The results for the traditional cut-based analysis
are presented in Sect.~\ref{sec:results}, and in
Sect.~\ref{sec:mva} we show how we can enhance signal
significance using multivariate techniques.
%
The robustness of our results under realistic pile-up
conditions expected at the HL-LHC is illustrated in
 Sect.~\ref{sec:pileup}.
%
Finally, in Sect.~\ref{sec:conclusions} we conclude and outline
how our results can be extended to estimate the accuracy
in the determination of trilinear coupling $\lambda$ and the constraints on
BSM scenarios.

>>>>

The measurement of double Higgs production will be one of the main
physics goals of the LHC program in its recently started high-energy
phase, as well as for its future high-luminosity upgrade (HL-LHC),
which aims to accumulate a total integrated
luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta,CMS:2013xfa}.
%
Higgs pair production is directly sensitive to the
Higgs trilinear coupling $\lambda$~\cite{baglio}, and thus 
provides crucial
information on the electroweak symmetry breaking mechanism.
%
It can also probe the underlying strength of the Higgs interactions
at high energies, and can be used to test the composite nature of the 
Higgs boson~\cite{Giudice:2007fh,Contino:2010mh}.
%
While Standard Model (SM) cross-sections are small,
many Beyond the SM (BSM)
scenarios predict enhanced rates for double Higgs production, and
thus searches for this process have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
and will continue at Run II.
%
In addition, Higgs pair production will also be of
crucial relevance at
any future high-energy 
collider, either at a 100 TeV circular machine~\cite{Barr:2014sga,Papaefstathiou:2015iba,Azatov:2015oxa} or at
a linear or circular electron-positron collider~\cite{Contino:2013gna}.

Analogously to single Higgs production~\cite{Dittmaier:2012vm}, 
in the SM the dominant mechanism for the production of a pair of
Higgs bosons at the LHC is 
gluon fusion (see Ref.~\cite{baglio,Frederix:2014hta} and
references therein).
%
For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the
next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once NNLL corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in gluon fusion have been performed for several different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
%
While these studies differ in their qualitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$
will only be achieved from the combination of various final states.

In addition to the gluon-fusion production mode, Higgs pairs
can also be produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes $hhW$ and $hhZ$~\cite{Barger:1988jk,baglio}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
Concentrating on the SM dynamics of Higgs pair production
in different channels, several studies
have investigate the interplay of various kinematical
distributions towards the optimisation of the
extraction of $\lambda$ from the measured
cross-sections, as well as the improvement
in the signal modeling taking into account
higher-order corrections and theoretical
uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
%

@@

In the context of SM production,
the main advantage of the $b\bar{b}b\bar{b}$ final state is the
enhancement of the signal yield
from the large branching fraction of Higgs bosons into bottom-anti-bottom
pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
%
However, a measurement in this channel
needs to deal with an overwhelming QCD multi-jet background.
%
Recent studies of Higgs pair production in this
final state~\cite{Wardrope:2014kya,deLima:2014dta}
estimate that, for an integrated
luminosity of
$\mathcal{L}_{\rm int}$=3000 fb$^{-1}$,
a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
%
While irreducible backgrounds, such as $4b$ and
$t\bar{t}$, are included in these analysis, the contribution
from reducible processes, such as $bbjj$ and
$jjjj$, which can fake the signal when 
light jets are mistagged as $b$-jets, are not accounted for.
%
As will show, this approximation is not justified since, both due to
combinatorics and to $b$-quark radiation in the
parton shower, the
contribution of the $2b2j$ and $4j$ backgrounds can become comparable or even larger
than the irreducible $4b$ component.

In this work, we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $b\bar{b}b\bar{b}$ final state.
%
 Our strategy is based on a combination of traditional cut-based
 methods with multivariate analysis (MVA),
 leading to a substantial
  enhancement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from mistags of
  light and charm jets.
  %
  We also model the impact of the pile-up (PU) effects expected at the
  HL-LHC by means of the {\tt SoftKiller} PU subtraction
  method~\cite{Cacciari:2014gra}.
  %
  By combining the contribution from
 the different event categories
  we achieve a total signal significance of $S/\sqrt{B}\simeq 4.0$
  for $\mathcal{L}_{\rm int}$=3000 fb$^{-1}$.
%
  These results emphasize the crucial importance that the $b\bar{b}b\bar{b}$ final state
  has for studies of Higgs pair production and for the determination of
  $\lambda$, as well as the advantages of the use of modern statistical
  analysis methods.

The structure of this paper is the following.
%
In Sect.~\ref{mcgeneration} we discuss the modeling of the signal
and background processes using Monte Carlo event generators.
%
In Sect.~\ref{sec:analysis}
we introduce our analysis strategy, and in particular
the classification of each individual event into
different categories according to their topology.
%
The results for the traditional cut-based analysis
are presented in Sect.~\ref{sec:results}, and in
Sect.~\ref{sec:mva} we show how we can enhance signal
significance using multivariate techniques.
%
The robustness of our results under realistic pile-up
conditions expected at the HL-LHC is illustrated in
....
%
Finally, in Sect.~\ref{sec:conclusions} we conclude and outline
how our results can be extended to estimate the accuracy
in the determination of trilinear coupling $\lambda$ and the constraints on
BSM scenarios.

### 2015-12-07 paper/sec-mcsamples.tex
yet more work on the paper
Implemented comments from Nathan

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
gluon-gluon-fusion Higgs boson pair production including the effects
of the
exact form factors for the top triangle and box loops at leading
order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that since recently it is possible to compute also
loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of using specific
models~\cite{Hirschi:2015iia}.}
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same in the default model,
in particular we use $m_h=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value.
%
The calculation is performed in the
$n_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.
%
For the input parton distribution functions, we 
adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.

@@

    The total inclusive cross-section for this processes is
    known up to NNLO~\cite{deFlorian:2013jea}.
    %
Resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
leading to a moderate enhancement of the order of
few percent as compared to the fixed-order NNLO calculation.
%
Therefore, to achieve the correct higher-order value of the  integrated cross-section, we rescale our LO signal sample to match the
NNLO+NNLO inclusive cross-section.
%
This corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
in Table~\ref{tab:samples}.

%
Parton level signal events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea} version {\tt v8.201}.
%
We use the default settings for the modeling
of the underlying event (UE), multiple parton
interactions (MPI) and pile-up, by means
of the the Monash 2013 tune~\cite{Skands:2014pea},
with the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
%
We switched off hadronisation, since this allows a more transparent
modeling of our strategy for
$b$-tagging.
%
A complete simulation of $b$-tagging at the hadron level is difficult
to achieve without a full
detector simulator, which is beyond the scope of this work.

@@

In addition to the QCD multijet processes,
we also generate $t\bar{t}$ samples
in the fully hadronic final state, which lead to a
$2b4j$ signature that can
contribute due to light jet mistags.
%
This background processes leads a similar topology that
the corresponding QCD sample.
%
In this case,
we have used a value of the top quark mass of $m_t=173.2$ GeV.
%
Leptonic decays of top quarks can be removed by requiring
a lepton veto, and thus are not included here.

@@

At the generation level, the following mild
cuts are applied to
background events.
%
Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
in the central  rapidity
region with
$| \eta | \le 3.0$.
%
In addition, at the matrix-element level
all final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
%
We have checked that the generator-level cuts are loose enough to have
no influence over the analysis cuts.
%

The LO cross-sections,
number of generated events and the higher-order $K$-factors
applied to the signal and background
samples are collected in Table~\ref{tab:samples}.
%
We see that the $t\bar{t}$ and QCD $4b$ samples are of
the same order of magnitude, however, the former can be efficiently
reduced by using top quark reconstruction criteria.
%
The $bbjj$ cross-section is around factor 200 as compared to the
$4b$ result, however, as we will show,
due both to combinatorics and to $b$-quark radiation
during the parton shower it can be comparable or larger
than the irreducible QCD background.
%
 For top quark production, only the hadronic final state is generated.
 %

@@

In this work, we simulate the finite momentum resolution of the ATLAS and CMS
hadronic calorimeters by applying a Gaussian smearing of the transverse
momentum $p_T$ of all
final-state particles, before jet clustering,
with mean zero and standard deviation $\sigma_E$, that is
%
\be
\label{eq:smearing}
p_T^{(i)} \, \to \, p_T^{(i)\prime}= \lp 1+ r_i\cdot\sigma_E \rp\, p_T^{(i)} \, , \quad
i=1,\ldots,N_{\rm part} \, ,
\ee
with $r_i$ an univariate Gaussian random number, different for each
of the $N_{\rm part}$ particles in the event.
%
We take as baseline value a momentum smearing
factor of $\sigma_E=5\%$.
%

@@

Our modelling of detector simulation has been motivated
to lead to a mass resolution of
reconstructed Higgs candidates of around 10 GeV, consistent
with the hadronic mass resolutions of ATLAS and CMS.
%
In  Fig.~\ref{fig:higgs-mass-resolution} we show the
invariant mass distributions of the leading
Higgs candidate in signal events for the
resolved category (see Sects.~\ref{sec:analysis}
and~\ref{sec:results}), together with
a Gaussian fit,
used to determine the mass resolution.
%
We indeed  find a mass resolution of about 8\%, corresponding
    to around 10 GeV for $m_H=125$ GeV.
%
    For completeness, in Fig.~\ref{fig:higgs-mass-resolution}
    we also show the corresponding
    mass distributions of Higgs candidates
    in the case of $\la n_{\rm PU}\ra=80$ PU events
    subtracted with {\tt SoftKiller} (see Sect.~\ref{sec:pileup}).
    %
    In the case of PU, the mass resolution is increased to around 11\%, corresponding to
    14 GeV.
    %

>>>>

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
gluon-gluon-fusion Higgs boson pair production including the effects
of the
exact form factors for the top triangle and box loops at leading
order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that
  since recently it is possible to compute also
  loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of
  using specific
models~\cite{Hirschi:2015iia}.}
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same as in the default model,
in particular we use $m_h=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value, $\lambda=m_h^2/2v^2$, with $m_h=125$ GeV
the Higgs boson mass and $v\simeq 246$ GeV the Higgs vacuum expectation
value (vev).
%
The calculation is performed in the
$n_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.
%
For the input parton distribution functions, we 
adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.

@@

    The total inclusive cross-section for this processes is
    known up to NNLO~\cite{deFlorian:2013jea}.
    %
Resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
leading to a moderate enhancement of the order of
few percent as compared to the fixed-order NNLO calculation.
%
Therefore, to achieve the correct higher-order value of the  integrated cross-section, we rescale our LO signal sample to match the
NNLO+NNLL
inclusive cross-section.
%
This corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
in Table~\ref{tab:samples}.
%
Parton level signal events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea} version {\tt v8.201}.
%
We use the default settings for the modeling
of the underlying event (UE), multiple parton
interactions (MPI) and pile-up, by means
of the the Monash 2013 tune~\cite{Skands:2014pea},
with the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
%

@@

In addition to the QCD multijet processes,
we also generate $t\bar{t}$ samples
in the fully hadronic final state, which lead to a
$2b4j$ signature that can
contribute due to light jet mistags.
%
This background processes leads a similar topology that
the corresponding QCD sample.
%
Leptonic decays of top quarks can be removed by requiring
a lepton veto, and thus are not included here.
%
Single Higgs production processes, such as $Z(\to b\bar{b})h(\to b\bar{b})$
and $t\bar{t}h(\to b\bar{b})$, and electroweak backgrounds, such $Z(\to b\bar{b})b\bar{b}$,
are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
and thus not included in the present analysis.
%

@@

At the generation level, the following loose selection 
cuts are applied to
background events.
%
Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
in the central  rapidity
region with
$| \eta | \le 3.0$.
%
In addition, at the matrix-element level
all final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
%
We have checked that the generator-level cuts are loose enough to have
no influence over the analysis cuts.
%

The LO cross-sections,
number of generated events and the higher-order $K$-factors
applied to the signal and background
samples are collected in Table~\ref{tab:samples}.
%
We see that the $t\bar{t}$ and QCD $4b$ samples are of
the same order of magnitude, however, the former can be efficiently
reduced by using top quark reconstruction criteria.
%
The $bbjj$ cross-section is more than two orders
of magnitude larger as compared to the
$4b$ result, however, as we will show,
due both to combinatorics and to $b$-quark radiation
during the parton shower it can be comparable or larger
than the irreducible QCD background.
%
 For top quark production, only the hadronic final state is generated.
 %

@@

In this work, we simulate the finite energy resolution of the ATLAS and CMS
hadronic calorimeters by applying a Gaussian smearing of the transverse
momentum $p_T$ of all
final-state particles, before jet clustering,
with mean zero and standard deviation $\sigma_E$, that is
%
\be
\label{eq:smearing}
p_T^{(i)} \, \to \, p_T^{(i)\prime}= \lp 1+ r_i\cdot\sigma_E \rp\, p_T^{(i)} \, , \quad
i=1,\ldots,N_{\rm part} \, ,
\ee
with $r_i$ an univariate Gaussian random number, different for each
of the $N_{\rm part}$ particles in the event.
%
We take as baseline value a momentum smearing
factor of $\sigma_E=5\%$.
%

@@

Our modelling of detector simulation has been motivated
to lead to a mass resolution of
reconstructed Higgs candidates of around 10 GeV, consistent
with the hadronic mass resolutions of ATLAS and CMS.
%
In  Fig.~\ref{fig:higgs-mass-resolution} we show the
invariant mass distributions of the leading
Higgs candidate in signal events for the
resolved category (see Sects.~\ref{sec:analysis}
and~\ref{sec:results}), together with
a Gaussian fit,
used to determine the mass resolution.
%
We indeed  find a mass resolution of about 8\%, corresponding
    to around 10 GeV for $m_H=125$ GeV.
%
    For completeness, in Fig.~\ref{fig:higgs-mass-resolution}
    we also show the corresponding
    mass distributions of Higgs candidates
    in the case of $\la n_{\rm PU}\ra=80$ PU events
    subtracted with {\tt SoftKiller} (see Sect.~\ref{sec:pileup}).
    %
    In the case of PU, the mass resolution is degraded down to
    around 11\%, corresponding to 
    14 GeV.
    %
